Case Study (McKenna)

### 2020-05-20 Code/mrp/Case Study (McKenna) .Rmd
Editing intro to case study

In this case study there are four classification variables choosen: age, income, ethnicity, gender, and state. Each vairbale is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).

>>>>

In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state. Each variable is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).
